%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Do not alter this block (unless you're familiar with LaTeX
\documentclass{article}[12pt]
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb,amsfonts, fancyhdr, color, comment, graphicx, environ, tikz}

\usepackage{mdframed}
\usepackage[shortlabels]{enumitem}
\usepackage{indentfirst}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}


\pagestyle{fancy}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{example}
\newtheorem{example}{Example}[section]
\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{question}{Question}[section]
\newtheorem{rules}{Rule}[section]
% prevent line break in inline mode
\binoppenalty=\maxdimen
\relpenalty=\maxdimen

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Fill in the appropriate information below

\rhead{Calculus} 
\chead{4-4 More Initial  Value Problems}
\begin{document}
\section{Warm-up}
\begin{enumerate}
\item My cat (Nox) knocked my mug off the counter. The counter is 3 feet high, and the mug fell (and broke) after 2 heart stopping seconds. Note that acceleration due to gravity is approximately 32 ft/$s^2$.
\begin{enumerate}
\item Find an equation that models the height of the mug $t$ seconds after Nox hit it.
\end{enumerate}
\vspace{4cm}
\item One of the lunar astronauts dropped a wrench from the top of the space module (12 meters above the surface of the moon). How long did it take for the wrench to hit the ground? (The acceleration due to gravity on the moon is 1.622m/$s^2$ down.)
\end{enumerate}
\vspace{4cm}
\section{Introduction}
This is probably the only part of calculus that might one day be close to useful, or at least vaguely applicable,  depending on what you do in life. So we're going to spend some more time on this, and hopefully it will be fun.
\section{The goal}
The goal is to create your own initial value problem. 
\section{Instructions}
\begin{enumerate}
\item First acquire the necessary materials:
\begin{itemize}
\item Tennis ball
\item Stopwatch (phones are perfect)
\item Recording device perhaps?
\end{itemize}
\item Now using the tools given to you, throw or drop the balls and measure how long it takes for the ball to fall. 
\item You now have different initial conditions. 
As a class, we will work through how to write equations modeling the path the tennis ball took. 
\end{enumerate}

\end{document}