%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Do not alter this block (unless you're familiar with LaTeX
\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb,amsfonts, fancyhdr, color, comment, graphicx, environ}

\usepackage{mdframed}
\usepackage[shortlabels]{enumitem}
\usepackage{indentfirst}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}


\pagestyle{fancy}


\newcommand{\units}{Please include units.}
% prevent line break in inline mode
\binoppenalty=\maxdimen
\relpenalty=\maxdimen

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Fill in the appropriate information below
\lhead{Name:}
\rhead{Calculus} 
\chead{\textbf{Test 4}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
In order to get full credit, please show your work for each question.
\begin{enumerate}
\item Evaluate the following integrals
\begin{enumerate}
\item $\int 32 x^{6}dx$
\vspace{4cm}
\item $\int 50e^{x}dx$
\vspace{4cm}
\item $\int \frac{1}{4}5^tdt$
\vspace{4cm}
\item $\int \sec^2(x)dx$
\vspace{4cm}
\end{enumerate}
\newpage
\item A tomato is thrown off the top of Carey Hall with an initial velocity of $10$ ft/sec. After 2 seconds, the tomato landed on the steps of Carey (Note this did not happen, I do not know how tall Carey Hall is). 
\begin{enumerate}
\item Write a function that gives the height of the tomato after $t$ seconds. Recall that acceleration due to gravity is given by 32 ft/$\text{sec}^2$. 
\vspace{4cm}
\item How tall is Carey Hall?
\vspace{2cm}
\end{enumerate}
\item When asked to evaluate $\int x^2dx$, a student gave the answer of $x^3/3+5$. 
\begin{enumerate}
\item Why is this answer incorrect?
\vspace{3cm}
\item What is the correct answer?
\end{enumerate}
\newpage
\item A nursery sells rosemary bushes after two years of growing and shaping. The growth rate is approximated by 
\[h'(t)=\frac{1}{3}t+3\] where $t$ is in years and $h'(t)$ is in inches/year. The seedlings are 2 inches tall when planted.
\begin{enumerate}
\item Find the height after $t$ years. 
\vspace{3cm}
\item How tall are the shrubs when they are sold?
\vspace{3cm}
\end{enumerate}
\item Provide three antiderivatives for the function $\frac{5}{x}+5$. 
\newpage
\item Evaluate the following integrals. 
\begin{enumerate}
\item $\int(x^4+3x+7)^{18}(4x^3+3)dx$
\vspace{3cm}
\item $\int(4y^3-3)e^{y^4-3y+5}dy$
\vspace{3cm}
\item $\int24(18t^2-\cos t)(6t^3-\sin t)^{23}dt$
\vspace{3cm}
\item $\int\frac{x^3+1}{(x^4+4x)^2}dx$
\vspace{3cm}
\item $\int(\cos(w)+12w^2)e^{\sin(w)+4w^3}dw$
\end{enumerate}
\end{enumerate}
\end{document}