%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Do not alter this block (unless you're familiar with LaTeX
\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb,amsfonts, fancyhdr, color, comment, graphicx, environ}

\usepackage{mdframed}
\usepackage[shortlabels]{enumitem}
\usepackage{indentfirst}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}


\pagestyle{fancy}


\newcommand{\units}{Please include units.}
% prevent line break in inline mode
\binoppenalty=\maxdimen
\relpenalty=\maxdimen

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Fill in the appropriate information below

\rhead{Calculus} 
\chead{\textbf{Test 4 REVIEW}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
This Test is question for question a similar replica of test 4 that will be given in class. 
\begin{enumerate}
\item Evaluate the following integrals
\begin{enumerate}
\item $\int 2 y^{12}dy$
\item $\int 75e^{t}dt$
\item $\int 2\ln(w)dw$
\item $\int -\csc^2(x)dx$
\end{enumerate}
\item A tomato is thrown off the top of Carey Hall with an initial velocity of $17$ ft/sec. After 1 second, the tomato landed on the steps of Carey (Note this did not happen, I do not know how tall Carey Hall is). 
\begin{enumerate}
\item Write a function that gives the height of the tomato after $t$ seconds. Recall that acceleration due to gravity is given by 32 ft/$\text{sec}^2$. 
\item How tall is Carey Hall?
\end{enumerate}
\item When asked to evaluate $\int x^7dx$, a student gave the answer of $x^8/8+700$. 
\begin{enumerate}
\item Why is this answer incorrect?
\item What is the correct answer?
\end{enumerate}
\item A nursery sells oregano plants after 1.5 years of growing and shaping. The growth rate is approximated by 
\[h'(t)=\frac{1}{9}t+1\] where $t$ is in years and $h'(t)$ is in inches/year. The seedlings are 3 inches tall when planted.
\begin{enumerate}
\item Find the height after $t$ years. 
\item How tall are the plants when they are sold?
\end{enumerate}
\item Provide three antiderivatives for the function $\frac{700}{x}+9$. 
\item Evaluate the following integrals. 
\begin{enumerate}
\item $\int(x^3+2x^2+6)^{10}(3x^2+4x)dx$
\item $\int(3y^2-4y)e^{y^3-2y^2+5}dy$
\item $\int17(14t^6 -\sin t)(2t^7+\cos t)^{16}dt$
\item $\int\frac{x+1}{x^8+8x}dx$
\item $\int(\cos(w)+2w)e^{\sin(w)+w^2}dw$
\end{enumerate}
\end{enumerate}
\end{document}