%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Do not alter this block (unless you're familiar with LaTeX
\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb,amsfonts, fancyhdr, color, comment, graphicx, environ}

\usepackage{mdframed}
\usepackage[shortlabels]{enumitem}
\usepackage{indentfirst}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}


\pagestyle{fancy}


\newcommand{\units}{Please include units.}
% prevent line break in inline mode
\binoppenalty=\maxdimen
\relpenalty=\maxdimen

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Fill in the appropriate information below
\lhead{Name:}
\rhead{Calculus} 
\chead{\textbf{Test 4 Makeup}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
In order to get full credit, please show your work for each question.
\begin{enumerate}
\item Evaluate the following integrals
\begin{enumerate}
\item $\int 16 x^{8}dx$
\vspace{4cm}
\item $\int \frac{1}{40}e^{x}dx$
\vspace{4cm}
\item $\int \frac{1}{3}2^tdt$
\vspace{4cm}
\item $\int \sec(x)\tan(x)dx$
\vspace{4cm}
\end{enumerate}
\newpage
\item A croissant is thrown off the top of the Eiffel Tower with an initial velocity of 17 meters/sec. After 10 seconds, the, the croissant landed on the ground.  
\begin{enumerate}
\item Write a function that gives the height of the croissant after $t$ seconds. Recall that acceleration due to gravity is given by 9.8 meters/$\text{sec}^2$. 
\vspace{4cm}
\item How tall is the Eiffel Tower? (round to a whole meter)
\vspace{2cm}
\end{enumerate}
\item A student is asked to evaluate $\int 3x^2dx$ and writes $x^3$. 
\begin{enumerate}
\item Why is this answer incorrect?
\vspace{3cm}
\item Solve the problem correctly:
\end{enumerate}
\newpage
\item A a willow hybrid tree grows very quickly in its early years, with a growth rate of 7 ft/year, or $h'(t)=7$, reaching 60 feet at  7 years. 
\begin{enumerate}
\item Find the height after $t$ years. 
\vspace{3cm}
\item How tall are these trees when planted?
\vspace{3cm}
\end{enumerate}
\item List three different anti-derivatives of $\frac{6}{x}+5x^2$
\newpage
\item Evaluate the following integrals. 
\begin{enumerate}
\item $\int(x^2+9x+12)^{20}(2x+9))dx$
\vspace{3cm}
\item $\int(3y^2+5)e^{y^3+5y}dy$
\vspace{3cm}
\item $\int14(12t-\sin t)(6t^2+\cos t)^{13}dt$
\vspace{3cm}
\item $\int\frac{x^2+1}{(x^3+3x)^4}dx$
\vspace{3cm}
\item $\int(\cos(w)+6w^2)e^{\sin(w)+2w^3}dw$
\end{enumerate}
\end{enumerate}
\end{document}